### 2016-03-28 ms_oviemission.tex
OVI and Lya emissivity paper

\documentclass[useAMS,usenatbib]{mn2e}
\input psfig.sty
\usepackage{array}
%\usepackage{graphicx}
%\usepackage{epstopdf}

\voffset=-0.8in

\def \gas {\textsc{gasoline}}
\def \gastwo {\textsc{ESF-gasoline2}}
\def \changa {\textsc{changa}}
\def \mean#1{\left< #1 \right>}

%%MISC
\def \aj {AJ}
\def \apj {ApJ}
\def \apjl {ApJL}
\def \mnras {MNRAS}
\def \apjs {ApJS}
\def \aap {A\&A}
\def \nat {Nature}
\def \pasp {PASP}
\def \na {NewA}

\def \etal {et~al.~}
\def \eg{e.g.}
\def \Section{\S}
\def \spose#1{\hbox  to 0pt{#1\hss}}  
\def \lta{\mathrel{\spose{\lower 3pt\hbox{$\sim$}}\raise  2.0pt\hbox{$<$}}}
\def \gta{\mathrel{\spose{\lower  3pt\hbox{$\sim$}}\raise 2.0pt\hbox{$>$}}}
\def \ion#1#2{#1{\footnotesize{#2}}\relax}
\def \ha       {H$\alpha$}
\def \hi       {\ion{H}{I}}
\def \hii      {\ion{H}{II}}
\def \oii      {[\ion{O}{II}]}

%%UNITS
\def \kmsmpc {\>{\rm km}\,{\rm s}^{-1}\,{\rm Mpc}^{-1}}
\def \kms {\ifmmode  \,\rm km\,s^{-1} \else $\,\rm km\,s^{-1}  $ \fi }
\def \kpc {\ifmmode  {\rm kpc}  \else ${\rm  kpc}$ \fi  }  
\def \hkpc {\ifmmode  {h^{-1}\rm kpc}  \else ${h^{-1}\rm kpc}$ \fi  }  
\def \hMpc {\ifmmode  {h^{-1}\rm Mpc}  \else ${h^{-1}\rm Mpc}$ \fi  }  
\def \Msun {\ifmmode \rm M_{\odot} \else $\rm M_{\odot}$ \fi}
\def \hMsun {\ifmmode h^{-1}\,\rm M_{\odot} \else $h^{-1}\,\rm M_{\odot}$ \fi}
\def \hhMsun {\ifmmode h^{-2}\,\rm M_{\odot}\else $h^{-2}\,\rm M_{\odot}$ \fi}
\def \Lsun {\ifmmode L_{\odot} \else $L_{\odot}$ \fi} 
\def \hhLsun {\ifmmode h^{-2}\,\rm L_{\odot} \else $h^{-2}\,\rm L_{\odot}$ \fi}

%%COSMOLOGY

\def\LCDM{$\Lambda$CDM }
\def \LCDM {\ifmmode \Lambda{\rm CDM} \else $\Lambda{\rm CDM}$ \fi}
\def \sig8 {\ifmmode \sigma_8 \else $\sigma_8$ \fi} 
\def \Omegam {\ifmmode \Omega_{\rm m} \else $\Omega_{\rm m}$ \fi} 
\def \Omegab {\ifmmode \Omega_{\rm b} \else $\Omega_{\rm b}$ \fi} 
\def \Omegar {\ifmmode \Omega_{\rm r} \else $\Omega_{\rm r}$ \fi} 
\def \fbar {\ifmmode f_{\rm bar} \else $f_{\rm bar}$ \fi} 
\def \OmegaL {\ifmmode \Omega_{\rm \Lambda} \else $\Omega_{\rm \Lambda}$\fi} 
\def \Deltavir {\ifmmode \Delta_{\rm vir} \else $\Delta_{\rm vir}$ \fi}
\def \rhocrit {\ifmmode \rho_{\rm crit} \else $\rho_{\rm crit}$ \fi}

%DARK MATTER
\def \rs {\ifmmode r_{\rm s} \else $r_{\rm s}$ \fi} 
\def \rh {\ifmmode r_{\rm h} \else $r_{\rm h}$ \fi} 
\def \Rvir {\ifmmode R_{\rm vir} \else $R_{\rm vir}$ \fi}
\def \Vvir {\ifmmode V_{\rm  vir} \else  $V_{\rm vir}$  \fi} 
\def \Vmax {\ifmmode V_{\rm  max} \else  $V_{\rm max}$  \fi} 
\def \Mvir {\ifmmode M_{\rm  vir} \else $M_{\rm  vir}$ \fi}  
\def \Mhalo {\ifmmode M_{\rm halo} \else $M_{\rm  halo}$ \fi}  
\def \Nvir {\ifmmode N_{\rm  vir} \else $N_{\rm  vir}$ \fi}  
\def \Jvir {\ifmmode J_{\rm vir} \else $J_{\rm vir}$ \fi} 
\def \Evir {\ifmmode E_{\rm vir} \else $E_{\rm vir}$ \fi} 
\def \lam {\ifmmode \lambda  \else $\lambda$ \fi} 
\def \lamp {\ifmmode \lambda^{\prime} \else $\lambda^{\prime}$  \fi} 
\def \lampc {\ifmmode \lambda^{\prime}_{\rm c} \else
  $\lambda^{\prime}_{\rm c}$  \fi}

\def \xoff {\ifmmode x_{\rm off} \else $x_{\rm off}$ \fi}
\def \rhorms {\ifmmode \rho_{\rm rms} \else $\rho_{\rm rms}$ \fi}
\def \qbar {\ifmmode \bar{q} \else $\bar{q}$ \fi}

%%BARYONS
\def \Mb {\ifmmode M_{\rm b} \else $M_{\rm b}$ \fi} 
\def \eSF {\ifmmode \epsilon_{\rm SF} \else $\epsilon_{\rm SF}$ \fi} 
\def \Md {\ifmmode M_{\rm d} \else $M_{\rm d}$ \fi} 
\def \Mg {\ifmmode M_{\rm g} \else $M_{\rm g}$ \fi} 
\def \Rb {\ifmmode R_{\rm b} \else $R_{\rm b}$ \fi} 
\def \Rd {\ifmmode R_{\rm d} \else $R_{\rm d}$ \fi} 
\def \Rg {\ifmmode R_{\rm g} \else $R_{\rm g}$ \fi} 
\def \mgal {\ifmmode m_{\rm gal} \else $m_{\rm gal}$ \fi} 
\def \rj {\ifmmode {\cal R}_j \else ${\cal R}_j$ \fi} 
\def \lamgal {\ifmmode \lambda_{\rm gal} \else $\lambda_{\rm gal}$ \fi} 
\def \Vcirc {\ifmmode V_{\rm circ} \else $V_{\rm circ}$ \fi} 
\def \Vrot {\ifmmode V_{\rm rot} \else $V_{\rm rot}$ \fi} 
\def \Vflat {\ifmmode V_{\rm flat} \else $V_{\rm flat}$ \fi} 
\def \Mstar {\ifmmode M_{\rm star} \else $M_{\rm star}$ \fi} 
\def \Mgas {\ifmmode M_{\rm gas} \else $M_{\rm gas}$ \fi} 
\def \Mbar {\ifmmode M_{\rm bar} \else $M_{\rm bar}$ \fi}

%%MASS-TO-LIGHT RATIOS
\def \DeltaIMF {\ifmmode \Delta_{\rm IMF} \else $\Delta_{\rm IMF}$ \fi}

\def \VV {\ifmmode V_{\rm 2.2}/V_{200} \else $V_{2.2}/V_{200}$ \fi} 
\def \dvr {\ifmmode \partial_{\rm VR} \else $\partial_{\rm VR}$ \fi}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[OVI Emssivity] {}

\author[Zhang et al.]{Shuinai Zhang$^{1}$\thanks{snzhang@pmo.ac.cn}, Liang Wang$^{1,3}$,Taotao Fang$^{2}$, Li Ji$^{1}$,
\newauthor{Thales Gutcke$^3$, Andrea V. Macci\`o$^{3,4}$}, Xi Kang$^{1}$\\
$^1$Purple Mountain Observatory, 2 West Beijing Road, Nanjing 210008, China\\
$^2$Xiamen Univeristy \\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
$^4$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE}
\begin{document}

\date{to be submitted to }

\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2016}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
  We use the NIHAO galaxy formation simulations to study ultra-violet (UV)
  emission from circum-galactic medium (CGM) in galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses. We analyze the spatially-extended structures of emission lines
  from OVI and Ly$alpha$.
\end{abstract}

\begin{keywords}
  galaxies: evolution -- galaxies: formation -- galaxies: dwarf -- galaxies: spiral -- 
  methods: numerical -- cosmology: theory
\end{keywords}

\setcounter{footnote}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 1: INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

This paper is organized as follows: The cosmological hydrodynamical
simulations and the methodology for computing metal line emission
are briefly described in  \S\ref{sec:method}; In \S\ref{sec:results} 
we present the results including the Ly$alpha$ and OVI emission map,
surface brightness and luminosity evolutions of all galaxies in NIHAO
sample; \S\ref{sec:sum} gives discussion and  summary of our
results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 2 METHODOLOGY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology} 
\label{sec:method}

\subsection{Simulations}
\label{sec:sims}

The simulations studied in this work are from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project \citep{Wang15}.  
The halos to be re-simulated with baryons have been extracted from 
3 different pure N-body simulations with a box size of 60, 20 and 
15 $h^{-1}$ Mpc respectively\citet{Dutton14}. 
All halos across the whole mass range with typically a million dark
matter particles inside the virial radius of the target halo at 
redshift $z=0$.  
We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.

We use the SPH hydrodynamics code {\sc gasoline} \citep{Wadsley04},
with a revised treatment of  hydrodynamics as described in
\citet{Keller14}.  The code includes a subgrid model for turbulent
mixing of metal and energy \citep{Wadsley08}, heating and cooling
include photoelectric heating of dust grains, ultraviolet (UV) heating
and ionization and  cooling due to hydrogen, helium and metals
\citep{Shen10}.  The star formation and feedback modeling follows what
was used in the MaGICC simulations \citep{Stinson13}.  There are two
small changes in NIHAO simulations: The change in  number of neighbors
and the new combination of softening length and  particle mass means
the threshold for star formation increased from  9.3 to 10.3
cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
  ESF}$, from 0.1 to 0.13.  The more detail on star formation and
feedback modeling can be found in \citet{Wang15}.

\subsection{Emissivity Calculation}
\label{sec:emis}

We first assign the number densities and temperatures of all gas particles
inside $2 R_{\rm vir}$ to $200\times 200 \times 200$ grids according SPH
spline kernel \citep{Monaghan85}:
\begin{equation}
W\left(r,h\right) = \frac{8}{\pi h^3}
  %\begin{cases}
  %1-6\left(\frac{r}{h}\right)^2+6\left(\frac{r}{h}\right)^3, & \quad 0\leq\frac{r}{h}\leq\frac{1}{2},\\
  %2\left(1-\frac{r}{h}\right)^3, & \quad \frac{1}{2} < \frac{r}{h} \leq 1,\\
  %0, & \quad \frac{r}{h} >1.\\
  %\end{cases}
\end{equation}

The emissivities are computed as a function of gas temperature and

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 3 RESULTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 4: SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{sec:sum}

\section*{Acknowledgments}

{\sc Gasoline} was written by Tom Quinn and James Wadsley. Without
their contribution, this paper would have been impossible.
The simulations were performed on the {\sc theo} cluster of the
Max-Planck-Institut f\"ur Astronomie and the {\sc hydra} cluster at
the Rechenzentrum in Garching; and the Milky Way supercomputer, funded
by the Deutsche Forschungsgemeinschaft (DFG) through Collaborative
Research Center (SFB 881) "The Milky Way System" (subproject Z2),
hosted and co-funded by the J\"ulich Supercomputing Center (JSC). We
greatly appreciate the contributions of all these computing
allocations. AVM acknowledge support through the
Sonderforschungsbereich SFB 881 “The Milky Way System” (subproject A1)
of the German Research Foundation (DFG).  The analysis made use of the
pynbody package \citep{Pontzen13}.
%
The authors acknowledge support from the MPG-CAS through the
partnership programme between the MPIA group lead by AVM and the PMO
group lead by XK.
LW acknowledges support of the MPG-CAS student
programme.
XK acknowledge the support from NSFC project
No.11333008 and the ``Strategic Priority Research Program the Emergence
of Cosmological Structures'' of the CAS(No.XD09010000).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{}

%%AAAAAAAA

% Extended Hot Halos around Isolated Galaxies Observed in the ROSAT All-Sky Survey
\bibitem[Anderson et al.(2013)]{Anderson13} Anderson, M.~E., Bregman, J.~N., Dai, X.\ 2013, \apj, 762, 106

% Fundamental differences between SPH and grid methods
\bibitem[Agertz et al.(2007)]{Agertz07} Agertz, O., Moore, B., Stadel, J.\ 2007, \mnras, 380, 963

%%BBBBBBBB

%The Average Star Formation Histories of Galaxies in Dark Matter Halos
% from z = 0-8
\bibitem[Behroozi et al.(2013)]{Behroozi13} Behroozi, P.~S.,
  Wechsler, R.~H., \& Conroy, C.\ 2013, \apj, 770, 57

%A First Estimate of the Baryonic Mass Function of Galaxies
\bibitem[Bell et al.(2003)]{Bell03} Bell, E.~F., McIntosh, D.~H., Katz, N., Weinberg, M.~D.,\ 2003, \apj, 585, 117

% Multiscale Gaussian Random Fields and Their Application to Cosmological Simulations
%\bibitem[Bertschinger(2001)]{Bertschinger01} Bertschinger, E.\ 2001, 
%\apjs, 137, 1

% The Search for the Missing Baryons at Low Redshift
\bibitem[Bregman (2007)]{Bregman07}
Bregman, J.~N.\ 2007, ARAA, 45, 221

%% CCCCCCCC

%Where are the baryons
\bibitem[Cen \& Ostriker (1999)]{Cen09} 
Cen, R.~Y., Ostriker, J.~P.\ 1999, \apj, 514, 1

%% DDDDDDDD

%Dark halo response and the stellar initial mass function in early-type and late-type galaxies
\bibitem[Dutton et al.(2011)]{Dutton11} Dutton, A.~A., Conroy, 
  C., van den Bosch, F.~C., et al.\ 2011, \mnras, 416, 322

%The baryonic Tully-Fisher relation and galactic outflows
\bibitem[Dutton(2012)]{Dutton12} Dutton, A.~A.\ 2012,
  \mnras, 424, 3123

%Cold dark matter haloes in the Planck era: evolution of structural parameters for Einasto and NFW profiles
\bibitem[Dutton \& Macci{\`o}(2014)]{Dutton14} Dutton,
  A.~A., \& Macci{\`o}, A.~V.\ 2014, \mnras, 441, 3359

%% EEEEEEEEE

%% FFFFFFFFF

% The Cosmic Baryon Budget
\bibitem[Fukugita et al.(1998)]{Fukugita98} Fukugita, M., Hogan, C.~J., Peebles, P.~J.~F.\ 1998, \apj, 503, 518

%% GGGGGGGGG

%% HHHHHHHHH

%% JJJJJJJJJJJ

%% KKKKKKKKKKK

%A superbubble feedback model for galaxy simulations
\bibitem[Keller et al.(2014)]{Keller14} Keller, B.~W., Wadsley, 
  J., Benincasa, S.~M., \& Couchman, H.~M.~P.\ 2014, \mnras, 442, 3013

% Stellar mass -- halo mass relation and star formation efficiency in
% high-mass halos
\bibitem[Kravtsov et al.(2014)]{Kravtsov14} Kravtsov, A., 
Vikhlinin, A., \& Meshscheryakov, A.\ 2014, arXiv:1401.7329

%% LLLLLLLLL

%% MMMMMMMMM

% The Baryon Content of Cosmic Structures
\bibitem[McGaugh et al.(2010)]{McGaugh10} McGaugh, S.~S., 
Schombert, J.~M., de Blok, W.~J.~G., Zagursky, M.~J.\ 2010, \mnras,
708, 14

% A refined particle method for astrophysical problems
\bibitem[Monaghan \& Lattanzio(1985)]{Monaghan85} Monaghan, J.~J., Lattanzio, J.~C., 1985, \aap, 149, 135

% Galactic star formation and accretion histories from matching galaxies to dark matter haloes
\bibitem[Moster et al.(2013)]{Moster13} Moster, B.~P., Naab, T., 
\& White, S.~D.~M.\ 2013, \mnras, 428, 3121

%% NNNNNNNNN

%% OOOOOOOO

%% PPPPPPPPP

%Planck 2013 results. XVI. Cosmological parameters
\bibitem[the Planck Collaboration et  al.(2014)]{Planck14}
  Planck Collaboration, Ade, P.~A.~R., Aghanim, N., et al.\ 2014,
  \aap, 571, AA16

% A Budget and Accounting of Metals at z ~ 0: Results from the COS-Halos Survey
\bibitem[Peeples et al.(2014)]{Peeples14} Peeples, M.~S., Werk, J.~K., Tumlinson, J., et al.\ 2014, \apj, 786, 54

% Dark MaGICC: the effect of dark energy on disc galaxy formation. Cosmology does matter
%\bibitem[Penzo et al.(2014)]{Penzo14} Penzo, C., Macci{\`o}, 
%  A.~V., Casarini, L., Stinson, G.~S., \& Wadsley, J.\ 2014, \mnras, 442, 176

% The baryon content of the universe
\bibitem[Persic \& Salucci(1992)]{Persic92} Persic, M., Salucci, P.\ 1992, \mnras, 258, 14

%pynbody: N-Body/SPH analysis for python
\bibitem[Pontzen et al.(2013)]{Pontzen13} Pontzen, A., Ro{\v s}kar, R., Stinson, G., \& Woods, R.\ 2013, Astrophysics Source Code Library, 1305.002

%% RRRRRRRRRRR

%Evolution of the Mass-Metallicity Relations in Passive and Star-forming Galaxies from SPH-cosmological Simulations

%Multiphase smoothed-particle hydrodynamics
%\bibitem[Ritchie \& Thomas(2001)]{Ritchie01} Ritchie, B.~W.,
%  \& Thomas, P.~A.\ 2001, \mnras, 323, 743

%% SSSSSSSSSSSS

% The enrichment of the intergalactic medium with adiabatic feedback - I. Metal cooling and metal diffusion
\bibitem[Shen et al.(2010)]{Shen10} Shen, S., Wadsley, J., 
\& Stinson, G.\ 2010, \mnras, 407, 1581

% The Baryon Census in a Multiphase Intergalactic Medium: 30% of the Baryons May Still be Missing
\bibitem[Shull et al.(2012)]{Shull12}
Shull, J.~M., Smith, B.~D., Danforth, C.~W.\ 2012, \apj, 759, 23

%Making Galaxies In a Cosmological Context: the need for early stellar feedback
\bibitem[Stinson et al.(2013)]{Stinson13} Stinson, G.~S., Brook, 
C., Macci{\`o}, A.~V., et al.\ 2013, \mnras, 428, 129

%% TTTTTTTTTTT

% Not Dead Yet: Cool Circumgalactic Gas in the Halos of Early-type Galaxies
\bibitem[Thom et al.(2012)]{Thom12}
Thom, C., Tumlinson, J., Werk, J.~K.\ 2012, \apjl, 758, L41

% The Large, Oxygen-Rich Halos of Star-Forming Galaxies Are a Major Reservoir
% of Galactic Metals
\bibitem[Tumlinson et al.(2011)]{Tumlinson11} Tumlinson, J., Thom, C., Werk, J., et al.\ 2011, Science, 334, 948

% The COS-Halos Survey: Rationale, Design and a Census of Circumgalactic Neutral Hydrogen
\bibitem[Tumlinson et al.(2013)]{Tumlinson13} Tumlinson, J., Thom, C., Werk, J., et al.\ 2013, \apj, 777, 59

%% VVVVVVVVVVVV

%% WWWWWWWWWWWWWW

%Gasoline: a flexible, parallel implementation of TreeSPH
\bibitem[Wadsley et al.(2004)]{Wadsley04} Wadsley, J.~W., Stadel, 
J., \& Quinn, T.\ 2004, \na, 9, 137

%On the treatment of entropy mixing in numerical cosmology
\bibitem[Wadsley et al.(2008)]{Wadsley08} Wadsley, J.~W., 
Veeravalli, G., \& Couchman, H.~M.~P.\ 2008, \mnras, 387, 427

  %NIHAO project I: Reproducing the inefficiency of galaxy formation across cosmic time with a large sample of cosmological hydrodynamical simulations
\bibitem[Wang et al.(2015)]{Wang15} Wang, L., Dutton, A.~A.,  Stinson, G.~S., et al.\ 2015, \mnras, 454, 83

% The COS-Halos Survey: Keck LRIS and Magellan MagE Optical Spectroscopy
\bibitem[Werk et al.(2012)]{Werk12} Werk, J.~k., Prochaska, J.~X., Thom, C., et al.\ 2012, \apjs, 198, 3

% The COS-Halos Survey: An Empirical Description of Metal-line Absorption in the Low-redshift Circumgalactic Medium
\bibitem[Werk et al.(2013)]{Werk13} Werk, J.~k., Prochaska, J.~X., Thom, C., et al.\ 2013, \apjs, 204, 17

%The COS-Halos Survey: Physical Conditions and Baryonic Mass in the Low-redshift Circumgalactic Medium
\bibitem[Werk et al.(2014)]{Werk14} Werk, J.~k., Prochaska, J.~X., Thom, C., et al.\ 2014, \apj, 792, 8

%% YYYYYYYYYYYY

%% ZZZZZZZZZZZZZ

\end{thebibliography}

\label{lastpage}
\end{document}

### 2016-03-28 ms_oviemission.tex
uncomplete draft in 28 Mar

@@
 %\usepackage{epstopdf}
+\usepackage{amsmath}
 
@@
 
-\title[OVI Emssivity] {}
+\title[OVI Emssivity] {HI and OVI Emission from the Circum-Galactic Medium
+ with a large sample of cosmological hydrodynamical simulations}
 
-\author[Zhang et al.]{Shuinai Zhang$^{1}$\thanks{snzhang@pmo.ac.cn}, Liang Wang$^{1,3}$,Taotao Fang$^{2}$, Li Ji$^{1}$,
-\newauthor{Thales Gutcke$^3$, Andrea V. Macci\`o$^{3,4}$}, Xi Kang$^{1}$\\
+\author[Zhang et al.]{Shuinai Zhang$^{1}$\thanks{snzhang@pmo.ac.cn}, Liang Wang$^{1,3}$,Taotao Fang$^{2}$, Li Ji$^{1}$,Thales Gutcke$^3$, 
+\newauthor{Andrea V. Macci\`o$^{3,4}$, Xi Kang$^{1}$}\\
 $^1$Purple Mountain Observatory, 2 West Beijing Road, Nanjing 210008, China\\
-$^2$Xiamen Univeristy \\
+$^2$Xiamen Univeristy, Xiamen, China \\
 $^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
@@
   masses. We analyze the spatially-extended structures of emission lines
-  from OVI and Ly$alpha$.
+  from OVI and Ly$\alpha$.
 \end{abstract}
@@
 
+{\bf Why the CGM is important}
+
+The hot and cold gas phases were indicated by OVI and HI ions in observation
+commomly.
+
+{\bf What can we gain from  HI and OVI in CGM}
+
+\citet{Gutcke16} compared the column density profiles of OVI and HI
+in CGM with observations.
+
+{\bf What is the advantage of emssion line of HI and OVI}
+
+\citet{Sravan15} studied ultra-violet (UV) metal line emission from the CGM
+of high-redshift ($z=2-4$) galaxies using cosmological simulations from the 
+Feedback in Realistic Environments (FIRE) project.
+
 This paper is organized as follows: The cosmological hydrodynamical
@@
 are briefly described in  \S\ref{sec:method}; In \S\ref{sec:results} 
-we present the results including the Ly$alpha$ and OVI emission map,
+we present the results including the Ly$\alpha$ and OVI emission map,
 surface brightness and luminosity evolutions of all galaxies in NIHAO
@@
 
-We first assign the number densities and temperatures of all gas particles
-inside $2 R_{\rm vir}$ to $200\times 200 \times 200$ grids according SPH
-spline kernel \citep{Monaghan85}:
+We first assign the hydrogen number densities and temperatures of all gas 
+particles inside $2 \Rvir$ to $200\times 200 \times 200$ grids 
+according SPH spline kernel \citep{Monaghan85}:
 \begin{equation}
 W\left(r,h\right) = \frac{8}{\pi h^3}
-  %\begin{cases}
-  %1-6\left(\frac{r}{h}\right)^2+6\left(\frac{r}{h}\right)^3, & \quad 0\leq\frac{r}{h}\leq\frac{1}{2},\\
-  %2\left(1-\frac{r}{h}\right)^3, & \quad \frac{1}{2} < \frac{r}{h} \leq 1,\\
-  %0, & \quad \frac{r}{h} >1.\\
-  %\end{cases}
+  \begin{cases}
+  1-6\left(\frac{r}{h}\right)^2+6\left(\frac{r}{h}\right)^3,  &\quad 0\leq\frac{r}{h}\leq\frac{1}{2},\\
+  2\left(1-\frac{r}{h}\right)^3,  &\quad \frac{1}{2} < \frac{r}{h} \leq 1,\\
+  0,  &\quad \frac{r}{h} >1.\\
+  \end{cases}
 \end{equation}
+The distribution of emissivities are then computed as a function of 
+gas temperature and hydroden number density on each grid by bi-linearly 
+interplating the grids of emissivities generated using CLOUDY 
+({\bf version and citation}).
+The temperature of the grids are in the range $?? < T < ??$K in intervals of
+$\Delta \log_{10} T = ?.??$ and hydrogen number densities are in the range
+$?? < n_H < ?? {\rm cm}^{-3}$ in intervals of $\Delta \log_{10} n_H = ??$.
+The grids are computed at redshift z = 0 assuming gas is of solar metallicity,
+optical thin and {\bf blabla}.
 
-The emissivities are computed as a function of gas temperature and
+To compute the HI neutral fraction, like \citep{Gutcke16}, we used the 
+self-shielding approximation presented in \citep{Rahmati13}.
+{\bf say more detail about it}. Contrastly, To compute the OVI, the 
+self-shielding approximation is not necessary to consider. {\bf reason}
+
+\subsection{Luminosity Calculation}
+\label{sec:lum}
+
+In order to estimate the evolution of total OVI and HI luminosities inside
+$2 \Rvir$, we employ the grids 
+of emissivities computed since z=4 to present to evaluate the evolution of 
+luminosities of all galaxies in NIHAO sample from particle data directly.
+The method is similar to the one used by \citep{Sravan15}, the OVI and HI 
+luminosities of each gas particle are calculated as
+\begin{equation}
+L = \epsilon_{\odot}\left(z,n_H,T\right)\left(\frac{m_{gas}}{\rho_{gas}}\right)
+    \left(\frac{Z_{gas}}{Z_{\odot}}\right),
+\end{equation}
+where $m_{gas}$, $\rho_{gas}$ and $Z_{gas}$ are the mass, density and 
+metallicity of the gas particle, and $\epsilon_{\odot}\left(z,n_H,T\right)$
+is the emissivity interpolated bi-linearly from pre-computed grids of 
+emissivities with given redshift, hydrogen number density and temperature.
 
@@
 \label{sec:results}
+
+\subsection{OVI and HI Emissivity Maps and Radial Profile}
+\label{sec:map_rp}
+
+\subsection{Evolution of Luminosities}
+\label{sec:evo}
 
@@
 
+\bibitem[Gutcke et al.(2016)]{Gutcke16} Gutcke, T.~A., Stinson, G.~S., Macci{\`o}, A.~V., et al.\ 2016, arXiv:1602.06956
+
 %% HHHHHHHHH
@@
 
-%Evolution of the Mass-Metallicity Relations in Passive and Star-forming Galaxies from SPH-cosmological Simulations
-
-%Multiphase smoothed-particle hydrodynamics
-%\bibitem[Ritchie \& Thomas(2001)]{Ritchie01} Ritchie, B.~W.,
-%  \& Thomas, P.~A.\ 2001, \mnras, 323, 743
+%Impact of local stellar radiation on the H I column density distribution
+\bibitem[Rahmati et al.(2013)]{Rahmati13} Rahmati, A., Schaye, J., Pawlik, A.~H., Rai{\v c}evi{\'c}, M., 2013, MNRAS, 431,2261
 
@@
 Shull, J.~M., Smith, B.~D., Danforth, C.~W.\ 2012, \apj, 759, 23
+
+%Strongly Time-Variable Ultra-Violet Metal Line Emission from the Circum-Galactic Medium of High-Redshift Galaxies
+\bibitem[Sravan et al.(2015)]{Sravan15} Sravan, N., Faucher-Gigu{\`e}re, C.~-A., van de Voort, F., et al.\ 2015, arXiv:1510.06410
 

### 2016-03-29 ms_oviemission.tex
28 Mar uncompleted draft

@@
 \def \oii      {[\ion{O}{II}]}
+\def \ovi      {\ion{O}{VI}}
 
@@
 
-\title[OVI Emssivity] {HI and OVI Emission from the Circum-Galactic Medium
+\title[\hi{} and \ovi{} Emssivity] {\hi{} and \ovi{} Emission from the Circum-Galactic Medium
  with a large sample of cosmological hydrodynamical simulations}
@@
   masses. We analyze the spatially-extended structures of emission lines
-  from OVI and Ly$\alpha$.
+  from \ovi{} and \hi{}.
 \end{abstract}
@@
 
-The hot and cold gas phases were indicated by OVI and HI ions in observation
+The hot and cold gas phases were indicated by \ovi{} and \hi{} ions in observation
 commomly.
 
-{\bf What can we gain from  HI and OVI in CGM}
+{\bf What can we gain from  \hi{} and \ovi{} in CGM}
 
-\citet{Gutcke16} compared the column density profiles of OVI and HI
-in CGM with observations.
+\citet{Gutcke16} compared the column density profiles of \ovi{} and \hi{}
+in CGM of galaxies of the cosmologycal hydrodynamical simulation suite 
+NIHAO \citep{Wang15} with observations, studied the covering fraction of 
+dense \hi{}, looked at the shape of the CGM and its chemical composition.
+The simulations have a good agreement with observations and show observers
+and modellers can compare with them in future studies.
 
-{\bf What is the advantage of emssion line of HI and OVI}
+However, the works mentioned above all relate to the absorption lines of
+\hi{} and \ovi{}, there are rare simulations comparing the emission lines
+of them with observations.
+{\bf What is the advantage of emssion line of \hi{} and \ovi{}}
 
@@
 Feedback in Realistic Environments (FIRE) project.
+For each simulation, they predicted the emission from multiple metal lines
+including \hi{} and \ovi{}, and found more massive haloes are on average 
+more UV-luminous and the UV metal line emission is primarily from collisionally
+ionized gas and strongly time variable. The high UV-luminous event correspond
+high star formation and \ion{C}{III}, \ion{Si}{III}, \ion{C}{IV} and \ion{Si}{IV}
+should be detectable by current and upcoming intergral field spectrographs such
+as the Multi Unit Spectroscopic Explorer (MUSE{\bf citation}).
+
+In this paper we investigate the CGM \ovi{} and \hi{} emissivity distribution
+and shape in Numerical Investigation of a Hundred Astrophysical Objects,
+NIHAO \citep{Wang15} project.
+NIHAO project produced nearly 100 hydrodynamical, cosmological zoom-in galaxies
+across a range in mass from
 
@@
 are briefly described in  \S\ref{sec:method}; In \S\ref{sec:results} 
-we present the results including the Ly$\alpha$ and OVI emission map,
+we present the results including the \hi{} and \ovi{} emission map,
 surface brightness and luminosity evolutions of all galaxies in NIHAO
@@
 
-The simulations studied in this work are from the NIHAO (Numerical
-Investigation of a Hundred Astrophysical Objects) project \citep{Wang15}.  
+The simulations studied in this work are from the NIHAO project \citep{Wang15}.  
 The halos to be re-simulated with baryons have been extracted from 
@@
 
-To compute the HI neutral fraction, like \citep{Gutcke16}, we used the 
+To compute the \hi{} neutral fraction, like \citep{Gutcke16}, we used the 
 self-shielding approximation presented in \citep{Rahmati13}.
-{\bf say more detail about it}. Contrastly, To compute the OVI, the 
+{\bf say more detail about it}. Contrastly, To compute the \ovi{}, the 
 self-shielding approximation is not necessary to consider. {\bf reason}
@@
 
-In order to estimate the evolution of total OVI and HI luminosities inside
+In order to estimate the evolution of total \ovi{} and \hi{} luminosities inside
 $2 \Rvir$, we employ the grids 
@@
 luminosities of all galaxies in NIHAO sample from particle data directly.
-The method is similar to the one used by \citep{Sravan15}, the OVI and HI 
+The method is similar to the one used by \citep{Sravan15}, the \ovi{} and \hi{} 
 luminosities of each gas particle are calculated as
@@
 
-\subsection{OVI and HI Emissivity Maps and Radial Profile}
+\subsection{\protect\ovi{} and \protect\hi{} Emissivity Maps and Radial Profile}
 \label{sec:map_rp}

### 2016-05-03 ms_oviemission.tex
add context about simulation in introduction

@@
 
-{\bf Why the CGM is important}
+A complete galaxy formation model does not only require the understanding
+of galactic components, such as stars and interstellar medium (ISM),
+but also the gaseous medium surrounded galaxies and extended to virial
+radius and beyond, the circumgalactic medium (CGM) namely.
+The galactic components dominate the energy output of the system,
+and always be focused by baryon counting \citep{Bell03}.
+Compared to the cosmological baryonic fraction $\Omega_b/\Omega_m$,
+stars and ISM come up significantly short on baryons. 
+If we include the hot X-ray halo gas \citep{Baldry08,Yang09,
+McGaugh10,Anderson10,Gupta12,Fang13}, the fracion is still under
+the prediction from the cosmic baryonic fraction.
 
-The hot and cold gas phases were indicated by \ovi{} and \hi{} ions in observation
-commomly.
+Galaxies have possibility apparently to exhibit a diffuse baryonic
+content within CGM ({\bf citation}) which is observed via UV absorption
+lines and has much lower temperature and density \citep{Werk13}.
+Such CGM cannot be traced directly by X-ray emission or any other
+radiative emission process.
+The installation of the Cosmic Origins Spectrograph (COS) greatly
+increased the capability of UV spectroscopy on the Hubble space
+Telescope (HST) platform (e.g. Savage et al. 2010), enabling the
+use of fainter quasar targets illuminating foreground galactic
+haloes.
+COS-Halos \citep{Tumlinson11, Thom12, Werk12, Werk13} has been 
+working to investigate 
+the properties of this elusive multiphase medium.
+One of COS-Halos results demonstrated CGM is a large reservior
+of baryons extanding far beyond the stellar disk of the galaxy.
+This significant reservoir of halo gas clearly plays a central 
+role in the cycling of baryons into and our of a galaxy, 
+regulating this growth.
 
-{\bf What can we gain from  \hi{} and \ovi{} in CGM}
-
+A number of large volume simulations \citep{Ford13, Ford15, Suresh15, Oppenheimer16} and 
+zoom-in cosmological simulations \citep{Stinson12,Hummels13,Shull14} have 
+investigated the properties of CGM and the link between 
+galaxies and their metal-enriched CGM.
+\citet{Ford15} do not include Active Galactic Nucleus (AGN) and do not
+reproduce the \ovi{} bimodality, while \citet{Suresh15b} argue that
+AGN feedback can remove the CGM around passive galaxies then reduce
+the \ovi{} column densities around  passive galaxies.
 \citet{Gutcke16} compared the column density profiles of \ovi{} and \hi{}
@@
 
-However, the works mentioned above all relate to the absorption lines of
-\hi{} and \ovi{}, there are rare simulations comparing the emission lines
-of them with observations.
-{\bf What is the advantage of emssion line of \hi{} and \ovi{}}
+Absorption line measurements have several limitations. 
+Firstly, suitable background sources are rare so that there is 
+typically only one or no background sight line per foreground
+galaxy({\bf citation}). Because the area covered scales as the 
+square of the impact parameter, the resulting measurements 
+preferentially probe large impact parameters from foreground 
+galaxies.
+Finally, because of the 1D nature of absorption line constraints
+it is often unclear what physical structure are probed.
+Intergral field measurement of emission lines are complementary 
+to absorption line measurements.
+In particular, they allow us to directly obtain a 3D picture
+of the distribution of gas in the CGM by combining the 2D map of
+emission on the sky with line-of-sight velocity information.
 
@@
 
+% Do Hot Haloes Around Galaxies Contain the Missing Baryons?
+\bibitem[Anderson \& Bregman (2010)]{Anderson10} Anderson, M.~E., Bregman, J.~N.\ 2010, \apj, 714, 320
+
 % Extended Hot Halos around Isolated Galaxies Observed in the ROSAT All-Sky Survey
@@
 %%BBBBBBBB
+
+% On the galaxy stellar mass function, the mass-metallicity relation and the implied baryonic mass function
+\bibitem[Baldry et al.(2008)]{Baldry08} Baldry, I.~K., Glazebrook, K., Driver, S.~P.\ 2008, \mnras, 388, 945
 
@@
 
+% On the Hot Gas Content of the Milky Way Halo
+\bibitem[Fang et al.(2013)]{Fang13} Fang, T., Bullock, J., Boylan-Kolchin, M.\ 2013, \apj, 762, 20
+
+%
+\bibitem[Ford et al.(2013)]{Ford13} Ford, A.~B., Oppenheimer, B.~D., Dav{\`e}, R., et al.\ 2013, \mnras, 432, 89
+
+%
+\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2015, arXiv:1503.02084
+
 % The Cosmic Baryon Budget
@@
 
+% A Huge Reservoir of Ionized Gas around the Milky Way: Accounting for the Missing Mass
+\bibitem[Gupta et al. (2012)]{Gupta12} Gupta, A., Mathur, S., Krongold, Y., et al.\ 2012, \apj, 756L, 8
+
 \bibitem[Gutcke et al.(2016)]{Gutcke16} Gutcke, T.~A., Stinson, G.~S., Macci{\`o}, A.~V., et al.\ 2016, arXiv:1602.06956
@@
 %% HHHHHHHHH
+
+%
+\bibitem[Hummels et al.(2013)]{Hummels13} Hummels, C.~B., Bryan, G.~L., Smith, B.~D., et al.\ 2013, \mnras, 430,1548
 
@@
 %% OOOOOOOO
+
+%
+\bibitem[Oppenheimer et al,(2016)]{Oppenheimer16}
+Oppenheimer, B.~D., Crain, R.~A., Schaye, J., et al.\ 2016, arXiv:1603.05984
 
@@
 
+%
+\bibitem[Shull (2014)]{Shull14}
+Shull, J.~M.\ 2014, \apj, 784, 142
+
 %Strongly Time-Variable Ultra-Violet Metal Line Emission from the Circum-Galactic Medium of High-Redshift Galaxies
 \bibitem[Sravan et al.(2015)]{Sravan15} Sravan, N., Faucher-Gigu{\`e}re, C.~-A., van de Voort, F., et al.\ 2015, arXiv:1510.06410
+
+%
+\bibitem[Stinson et al.(2012)]{Stinson12} Stinson, G.~S., Brook, C., Prochaska, J.~X., et al.\ 2012, \mnras, 425,1270
 
@@
 C., Macci{\`o}, A.~V., et al.\ 2013, \mnras, 428, 129
+
+%
+\bibitem[Suresh et al.(2015b)]{Suresh15b} Suresh, J., Rubin, K.~H.~R., Kannan, R., et al.\ 2015, arXiv:1511.00687
 
@@
 
+% Galaxy Group in the SDSS DR4. III. The Luminosity and Stellar Mass Functions
+\bibitem[Yang et al.(2009)]{Yang09} Yang, X., Mo, H.~J., van den Bosch, F.~C.\ 2009, \apj, 695, 900
+
 %% ZZZZZZZZZZZZZ

### 2016-05-20 ms_oviemission.tex
add context about van de Voort (2012)

@@
 
-A number of large volume simulations \citep{Ford13, Ford15, Suresh15, Oppenheimer16} and 
+\hi{}  is mainly from cold gas 
+($T\approx 10^4$K), and therefore provides an excellent route to 
+detecting cold gas in CGM.
+In the other hand, most gas in CGM is in the warm or hot phase
+with temperature $T > 10^{4.5}$ K, either through photo-ionization,
+accretion shock or shock caused by galactic winds \citep{voort12}.
+Such dilute halo gas is at $T \sim 10^{4.5-7}$K, 
+the detection is dominated by metal lines for Z$>$0.1 Z$_{\odot}$ \citep{Wiersma09a}.
+
+A number of large volume simulations \citep{Ford13, Ford15, Suresh15, 
+Oppenheimer16} and 
 zoom-in cosmological simulations \citep{Stinson12,Hummels13,Shull14} have 
@@
 
-Absorption line measurements have several limitations. 
+Comparing with Absorption line measurement, in general, 
+emission from gas outside of galaxies is to faint to detect.
+However, Absorption line measurements have several limitations. 
 Firstly, suitable background sources are rare so that there is 
@@
 
+The next generation of spectrographs should be able to detect certain metal
+lines, so that several cosmological hydrodynamical simulations have quantified
+the expected emission from the warm-hot IGM
+\citep{Furlanetto04, Bertone10a, Bertone10b, Takei11, Bertone12,
+Frank12, Rocarelli12}.
+\citet{Voort13} employed several large cosmological hydrodynamical simulations
+from the OverWhelmingly Large Simulations (Owls) project \citep{Schaye10}
+to explore the possibility to 
+detect metal-line emission if the metallicity Z $>$ 0.1 Z$_\odot$.
+They found, at given detection limit, the proposed X-ray telescope and future UV
+telescope can detect various metal lines depending on halo mass.
 \citet{Sravan15} studied ultra-violet (UV) metal line emission from the CGM
@@
 
-% Multiscale Gaussian Random Fields and Their Application to Cosmological Simulations
-%\bibitem[Bertschinger(2001)]{Bertschinger01} Bertschinger, E.\ 2001, 
-%\apjs, 137, 1
+%
+\bibitem[Bertone et al.(2010a)]{Bertone10a} Bertone, S., Schaye, J., Dalla Vecchia, C., et al.\ 2010a, \mnras, 407, 544
+
+%
+\bibitem[Bertone et al.(2010b)]{Bertone10b} Bertone, S., Schaye, J., Booth, C.~M., et al.\ 2010b, \mnras, 408, 1120
+
+%
+\bibitem[Bertone \& Schaye (2012)]{Bertone12} Bertone, S., Schaye, J.\ 2012, \mnras, 419, 780
 
@@
 
+%
+\bibitem[Frank et al.(2012)]{Frank12} Frank, S., et al.\ 2012, \mnras, 420, 1731
+
 % The Cosmic Baryon Budget
 \bibitem[Fukugita et al.(1998)]{Fukugita98} Fukugita, M., Hogan, C.~J., Peebles, P.~J.~F.\ 1998, \apj, 503, 518
+
+%
+\bibitem[Furlanetto et al.(2004)]{Furlanetto04} Furlanetto, S.~R., Schaye, J., Springel, V., Hernquist, L.\ 2004, \apj, 606, 221
 
@@
 
+%
+\bibitem[Rocarelli et al.(2012)]{Rocarelli12} Rocarelli, M., Cappelluti, N., Borgani, S., et al.\ 2012, \mnras, 424, 1012
+
 %% SSSSSSSSSSSS
+
+%
+\bibitem[Schaye et al.(2010)]{Schaye10} Schaye, J., Dalla Vecchia, C., Booth, C.~M., et al.\ 2010, \mnras, 402, 1536
 
@@
 
+%
+\bibitem[Takei et al.(2011)]{Takei11} Takei, Y., et al.\ 2011, \apj, 734, 91
+
 % Not Dead Yet: Cool Circumgalactic Gas in the Halos of Early-type Galaxies
@@
 %% VVVVVVVVVVVV
+
+%
+\bibitem[van de Voort \& Schaye (2012)]{voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991
+
+%
+\bibitem[van de Voort \& Schaye (2013)]{Voort13} van de Voort, F., Schaye, J.\ 2012, \mnras, 430, 2688
 
@@
 
+%
+\bibitem[Wiersma et al. (2009a)]{Wiersma09a} Wiersma, R.~P.~C., Schaye, J., Smith, B.~D.\ 2009a, \mnras, 393, 99
+
 %% YYYYYYYYYYYY
